### 2013-05-22 Docs/visualization/visualization.tex
start of some file format documentation

>>>>

\subsection{the \boxlib\ file format}

\maestro\ stores the plotfile data in a hierarchical directory format,
with each level's data stored in a separate subdirectory.  Some meta-data
is stored in the top-level to help interpret the structure.  The basic format is:
\begin{itemize}
\item {\tt plt00000/}
  \begin{itemize}
    \item {\tt Header}
    \item {\tt job\_info}
    \item {\tt Level\_00/}
      \begin{itemize}
        \item {\tt Cell\_D\_00000}
        \item {\ldots}
        \item {\tt Cell\_H}
      \end{itemize}
    \item {\tt model\_cc\_00000}
    \item {\tt model\_ec\_00000}
  \end{itemize}
\end{itemize}
%
In the main directory, {\tt Header} contains the information required
to interpret the data stored on disk.  We describe this below.  The
{\tt job\_info} file is a plaintext file that contains a lot of
information about the run (where it was run, when it was run, compiler
options, runtime options, etc.).  It is not needed to interpret the
data.  Finally, the {\tt model\_cc\_00000} and {\tt model\_ec\_00000}
contain the \maestro\ basestate information for the cell-centered and
edge-centered basestate quantities respectively.  These files are not
typically used for visualization.

\subsubsection{\tt Header}

The main {\tt Header} is written by {\tt fabio\_ml\_multifab\_write\_d}
